Raman sideband cooling of single Na atoms to 3D vibrational ground state

### 2017-05-23 presentations/na_cool_paper/paper.tex
[presentations/na_cool_paper] minor update

Finally, another important feature of our setup is the strong AC starck shift in the excited state.
The deep trap that is needed to trap and image single Sodium atom creates a light shift on the

the deep trap needed to ... also creates a large differential ..., which makes it impossible to load .... The same effect also happens on OP causing not only ... but also .... due to the breakdown of excited state HF structure.... We use switching....

% * Loose confinement
% ** More heating
% ** Complex sideband spectrum
% ** Matrix element minimum
% * Trap depth limit due to switching
% * High occupation
% ** Need more cooling
% ** Trap anharmonicity

% * Loose confinement
% ** Use higher orders to cool

>>>>

<WIP>

Finally, the deep trap that is needed to trap and image single Sodium atom also creates
a very large AC Stark shift in the excited state.

% impossible to load without switching
% The same effect also happens on OP causing
% *   cannot address atom in different position at the same time
% *   breakdown of excited state HF structure
% use switching
